---
title: "codeModules"
output: github_document
---

[![Travis build status](https://travis-ci.org/statistikat/codeModules.svg?branch=master)](https://travis-ci.org/statistikat/codeModules)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## About

This R package consists of several [shiny modules](https://shiny.rstudio.com/articles/modules.html) that
return R code in the form of `reactive` characters. All those modules represent common operations regarding

* Import of data (`read.csv`, `read.xlsx`, `data()`, ...)
* Manipulation of data (rename columns, change column classes, filtering)
* export of data (`write.csv`, `write.xlsx`, ...)

## Usage

Always save the output from `callModule` into a variable when working with modules from this package.
The outputs can then be parsed as R code using `eval(parse(text = code()))` or `evalCode`.

```{r cars, eval = FALSE}
## context: server.R
code <- callModule(libData, id = "some_id", assignTo = "dt")
output$table <- renderTable({
  evalCode(code())
})

```

## Implemented Modules

* **libData**: read data from `R` packages using `utils::data`
* **readData**: read data from a file using `read.csv`, `read.xlsx` or others depending on the fileextension.
* **variableView** Rename columns, filter data and change column types. The ui is oriented on the "variable view" in SPSS
* **ggDownload** Download ggplot with custom height, width and filetype (`png`, `jpeg`, ...)
* **downloadTable** Download tables (usually `data.frames`) as `csv`, `xlsx`, `rds`.

## Other functions

* **renderCode/codeOutput** Show code with syntax highlighting in the UI.
* **evalCode** Warapper for `eval(parse(text = .))` with error pupups.
