---
title: "codeModules"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## About

This R package consists of several [shiny modules](https://shiny.rstudio.com/articles/modules.html) that
return R code in the form of `reactive` characters. All those modules represent common operations regarding

* Import of data (`read.csv`, `read.xlsx`, `data()`, ...)
* ~~Manipulation of data (either with `dplyr` or `data.table`)~~
* ~~export of data (`write.csv`, `read.xlsx`, ...)~~

## Usage

Always save the output from `callModule` into a variable when working with modules from this package.
The modules can then be parsed as R code using `eval(parse(text = code()))`.

```{r cars, eval = FALSE}
## context: server.R
code <- callModule(libData, assignTo = "dt")
output$table <- renderTable({
  eval(parse(text = code()))
  return(dt)
})

```

## Implemented Modules

* **libData**: read data from `R` packages using `utils::data`
* **readData**: read data from a file using `read.csv`, `read.xlsx` or others depending on the fileextension.
